ASHA 2023 Listening Effort Data Analysis

### 2023-10-29 ASHA 2023 Analysis/data_analysis.Rmd
streamlined code for phrase accuracy descriptives

intel_df <- data %>%
  dplyr::select(subject, trial, speaker, correct_words, target_number, rep_acc) %>%
  dplyr::distinct()

intel_byListener <- intel_df %>%
  dplyr::group_by(speaker, subject) %>%
  dplyr::summarize(Intelligibility = sum(correct_words)/sum(target_number)*100)

intel_byListener %>%
  dplyr::group_by(speaker) %>%
  dplyr::summarize("Mean Intelligibility" = mean(Intelligibility), SD = sd(Intelligibility))

@@

@@

rep_acc <- intel_df %>%
  dplyr::group_by(speaker, rep_acc) %>%
  dplyr::summarize(n = n()) %>%
  tidyr::pivot_wider(names_from = rep_acc,
                     values_from = n) %>%
  dplyr::mutate(percent_accurate = accurate/(accurate + inaccurate)*100)

rep_acc

>>>>

# Selecting variables needed to calculate mean speaker intelligibility
intel_df <- data %>%
  dplyr::select(subject, trial, speaker, correct_words, target_number, rep_acc) %>%
  dplyr::distinct()

# Calculating intelligibility for the control and ALS speaker for each listener
intel_byListener <- intel_df %>%
  dplyr::group_by(speaker, subject) %>%
  dplyr::summarize(Intelligibility = sum(correct_words)/sum(target_number)*100)

intel_byListener %>%
  dplyr::group_by(speaker) %>%
  dplyr::summarize("Mean Intelligibility" = mean(Intelligibility), SD = sd(Intelligibility)) %>%
  gt::gt() %>%
  gt::fmt_number(columns = c("Mean Intelligibility", SD),
                 decimals = 2) %>%
  gt::cols_label(speaker = "Speaker")

@@

For this analysis, we are only looking at the trials that listeners were able to accurately recognize (e.g. 100% intelligible to the listener). Therefore, we are looking at the proportion of trials for each speaker that listeners were able to accurately recognize compared to the total number of trials. Although our ALS speaker's intelligibility was fairly high, only about 49% of all the ALS speaker's trials were accurately recognized across listeners.

@@

intel_df %>%
  dplyr::group_by(speaker, rep_acc) %>%
  dplyr::summarize(n = n()) %>%
  tidyr::pivot_wider(names_from = rep_acc,
                     values_from = n) %>%
  dplyr::mutate(percent_accurate = accurate/(accurate + inaccurate)*100) %>%
  dplyr::ungroup() %>%
  gt::gt(rowname_col = "speaker") %>%
  gt::fmt_number(columns = percent_accurate,
                 decimals = 2) %>%
  gt::cols_label(accurate = "Accurate",
                 inaccurate = "Inaccurate",
                 percent_accurate = "Percent Accurate")

```
```{r, include = F, warning = F, message = F}

# removing unneeded items from the environment

rm(intel_byListener, intel_df)
